---
title: "SuckyCorp Sucky Model Analysis"
author: "Jennifer Grosz"
date: "3/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message = FALSE}
source('01_LoadDataQ1.R', local = FALSE)
```

# Q1: 
##For each the four products, how do the expected scores compare, under varying environmental conditions

Regression Analysis 1:
For the first objective, determining how the expected scores compare across varying environmental conditions, I ran a linear regression model to determine the associated effect of each Sucky model on total average score over all environments.

```{r, echo=FALSE}
## Average Score Regression Analysis
reg1 <- lm(averageScore ~ Agent, simResults)
export_summs(reg1)
```

My regression analysis resulted in the following statistically significant conclusions:
  *	The Sensing Sucky model scores an average of 69 points higher than the Non-Sensing Sucky Model, which is a total average score of 94 points.
  *	The Memory Sucky model scores an average of 122 points higher than the Non-Sensing Sucky Model, which is a total average score of 147 points.
  *	The Omniscient Sucky model scores an average of 173 points higher than the Non-Sensing Sucky Model, which is a total average score of 198 points.
```{r}
effect_plot(reg1, pred = 'Agent', plot.points = TRUE, x.label = "Sucky Models", y.label = "Average Score")
```


```{r, echo=FALSE}
########### Average Total Average Over All Environments
average_all_models_bar
```

Figure 1. 

Above in Figure 1 you will see the total average scores per agent calculated across all environmental conditions that supports the results found from the regression analysis conducted.

```{r}
all_models_average_table
```

Table 1.

Above in Table 1 you will see








```{r}

########### Low Dirt, High Walls
low_dirt_high_walls_all <- simResults %>%
  filter(Dirt == .1, Wall == .3)

all_models_low_high_bar <- ggplot(low_dirt_high_walls, aes(Agent, averageScore)) + 
  geom_bar(aes(fill = Agent), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "Average Scores by Sucky Model",
       subtitle = "Environment: Low Dirt, High Walls")

all_models_low_high_bar
```

```{r}
########### High Dirt, Low Walls
high_dirt_low_walls_all <- simResults %>%
  filter(Dirt == .3, Wall == .1)

all_models_high_low_bar <- ggplot(high_dirt_low_walls, aes(Agent, averageScore)) + 
  geom_bar(aes(fill = Agent), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y= element_blank()) +
  labs(title = "Average Scores by Sucky Model",
       subtitle = "Environment: High Dirt, Low Walls")

all_models_high_low_bar

```




```{r, echo=FALSE}
########################################### Supplemental 
########### Low Dirt, Low Walls
low_dirt_low_walls_all <- simResults %>%
  filter(Dirt == .1, Wall == .1)

all_models_low_low_bar <- ggplot(low_dirt_low_walls, aes(Agent, averageScore)) + 
  geom_bar(aes(fill = Agent), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "Average Scores by Agent",
       subtitle = "Low Dirt, Low Walls")

all_models_low_low_bar
########### High Dirt, High Walls
high_dirt_high_walls_all <- simResults %>%
  filter(Dirt == .3, Wall == .3)

all_models_high_high_bar <- ggplot(high_dirt_high_walls, aes(Agent, averageScore)) + 
  geom_bar(aes(fill = Agent), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "Average Scores by Agent",
       subtitle = "High Dirt, HighWalls")

all_models_high_high_bar
```




```{r, echo=FALSE, message=FALSE}
###### percent function
percent <- function(x, digits = 2, format = "f", ...) {      
  paste0(formatC(x, format = format, digits = digits, ...), "%")
}

############################################## Table Generation
############################ Total average scores over all environments per agent
avg_all_models <- avg_all_models %>%
  select(Agent, percentChange, DifferenceInPercentChange) %>%
  mutate('Performance Improvment' = case_when(
           percentChange == 0 ~ "Baseline Model",
           percentChange != 0 ~ percent(percentChange)),
         'Improvement Difference' = case_when(
           DifferenceInPercentChange == 0 ~ "Most Improved Model",
           DifferenceInPercentChange == -100 ~ "Baseline Model",
           DifferenceInPercentChange != 0 ~ percent(DifferenceInPercentChange))) %>%
  select(-percentChange, -DifferenceInPercentChange ) 

#sort based on sucky model
avg_all_models <- avg_all_models %>%
  arrange(Agent = c("Non-Sensing Sucky","Sensing Sucky","Memory Sucky", "Omniscient Sucky"))
# create table
all_models_average_table <- kable(avg_all_models,
      caption = "Total Average Results Over All Environments",
      booktabs = TRUE) %>% kable_styling(font_size = 7)
# ouptut table
all_models_average_table

############################################## Table Generation
############################# low dirt high walls
lowhigh_all <- low_dirt_high_walls_all %>%
  select(Agent, percentChange, DifferenceInPercentChange) %>%
   mutate('Performance Improvment' = case_when(
           percentChange == 0 ~ "Baseline Model",
           percentChange != 0 ~ percent(percentChange)),
         'Improvement Difference' = case_when(
           DifferenceInPercentChange == 0 ~ "Most Improved Model",
           DifferenceInPercentChange == -100 ~ "Baseline Model",
           DifferenceInPercentChange != 0 ~ percent(DifferenceInPercentChange))) %>%
  select(-percentChange, -DifferenceInPercentChange ) 

#sort based on sucky model
lowhigh_all <- lowhigh_all %>%
  arrange(Agent = c("Non-Sensing Sucky","Sensing Sucky","Memory Sucky", "Omniscient Sucky"))
# create table
all_models_low_high_table <- kable(lowhigh_all,
      caption = "Results from Environment with Low Dirt, High Walls",
      booktabs = TRUE) %>% kable_styling(font_size = 7)
#output table
all_models_low_high_table

############################################## Table Generation
################################ high dirt low walls
highlow_all <- high_dirt_low_walls_all %>%
  select(Agent, percentChange, DifferenceInPercentChange) %>%
  mutate('Performance Improvment' = case_when(
           percentChange == 0 ~ "Baseline Model",
           percentChange != 0 ~ percent(percentChange)),
         'Improvement Difference' = case_when(
           DifferenceInPercentChange == 0 ~ "Most Improved Model",
           DifferenceInPercentChange == -100 ~ "Baseline Model",
           DifferenceInPercentChange != 0 ~ percent(DifferenceInPercentChange))) %>%
  select(-percentChange, -DifferenceInPercentChange ) 

#sort based on sucky model
highlow_all <- highlow_all %>%
  arrange(Agent = c("Non-Sensing Sucky","Sensing Sucky","Memory Sucky", "Omniscient Sucky"))
# create table
all_models_high_low_table <- kable(highlow_all,
      caption = "Results from Environment with High Dirt, Low Walls",
      booktabs = TRUE) %>% kable_styling(position = "left", font_size = 7)
# output table
all_models_high_low_table

```





#Q2:
## For the most popular Memory Sucky model, what is the effect of raising and lowering the battery capacity?  Assume that adding more battery capacity does not affect the agent's performance, e.g. by slowing it down, it is just a matter of the cost of adding the additional battery capacity. 

```{r, echo=FALSE, message=FALSE}
### Load battery test data
####### 500 Battery Capacity
BatteryCapacity_500 <- read_csv("../01_Data/500BatteryCapacity.csv", col_names = FALSE) %>%
  rename(Agent = X1, Dirt = X2, Wall = X3, Score = X4) %>%
  group_by(Dirt, Wall) %>%
  summarize(average_score = mean(Score)) %>%
  ungroup() %>%
  mutate(battery_capacity = 500)
####### 1000 Battery Capacity
BatteryCapacity_1000 <- read_csv("../01_Data/1000BatteryCapacity.csv", col_names = FALSE) %>%
  rename(Agent = X1, Dirt = X2, Wall = X3, Score = X4)  %>%
  group_by(Dirt, Wall) %>%
  summarize(average_score = mean(Score))  %>%
  ungroup() %>%
  mutate(battery_capacity = 1000)
####### 1500 Battery Capacity
BatteryCapacity_1500 <- read_csv("../01_Data/1500BatteryCapacity.csv", col_names = FALSE) %>%
  rename(Agent = X1, Dirt = X2, Wall = X3, Score = X4)  %>%
  group_by(Dirt, Wall) %>%
  summarize(average_score = mean(Score)) %>%
  ungroup()  %>%
  mutate(battery_capacity = 1500)
####### 2000 Battery Capacity
BatteryCapacity_2000 <- read_csv("../01_Data/2000BatteryCapacity.csv", col_names = FALSE) %>%
  rename(Agent = X1, Dirt = X2, Wall = X3, Score = X4)  %>%
  group_by(Dirt, Wall) %>%
  summarize(average_score = mean(Score)) %>%
  ungroup()  %>%
  mutate(battery_capacity = 2000)
####### 250 Battery Capacity
BatteryCapacity_250 <- read_csv("../01_Data/250BatteryCapacity.csv", col_names = FALSE) %>%
  rename(Agent = X1, Dirt = X2, Wall = X3, Score = X4) %>%
  group_by(Dirt, Wall) %>%
  summarize(average_score = mean(Score)) %>%
  ungroup() %>%
  mutate(battery_capacity = 250)

## Tidy Data
# merge all battery capacity data into one data set
battery_df <- rbind(BatteryCapacity_500, BatteryCapacity_1000, BatteryCapacity_1500, BatteryCapacity_2000, BatteryCapacity_250)

### baseline
baseline2 <- battery_df %>%
  filter(battery_capacity == 500) %>%
  mutate(baseline_score = average_score,
         Agent = "Memory Sucky") %>%
  select(-average_score, -battery_capacity)

battery_df <- left_join(battery_df, baseline2, by = c("Dirt", "Wall"))

battery_df <- battery_df %>%
  mutate(percentChange = ((average_score - baseline_score)/baseline_score*100)) %>%
  group_by(Dirt, Wall) %>%
  # identify model with largest improvement in score
  mutate(MostImprovedScore = max(percentChange),
         # identify most improved model
         MostImprovedAgent = case_when(
         percentChange == MostImprovedScore ~ battery_capacity),
         # calculate difference in improvement of scores from most improved model
         DifferenceInPercentChange = 
           ((percentChange - MostImprovedScore)/MostImprovedScore)*100) %>%
  ungroup() %>%
  mutate(battery_capacity = factor(battery_capacity))



############## Total average over all environments
# total agent average
totalaverage <- battery_df %>%
  group_by(battery_capacity) %>%
  mutate(totalaverage = mean(average_score)) %>%
  distinct(battery_capacity, totalaverage) %>%
  ungroup()

# baseline total agent average
base2 <- totalaverage %>%
  filter(battery_capacity == 500) %>%
  mutate(baseline_totalaverage = totalaverage) %>%
  select(-battery_capacity, -totalaverage)

totalaverage <- totalaverage %>%
  # add baseline score back to data
  mutate(baseline_totalaverage = base2$baseline_totalaverage,
    percentChange = ((totalaverage - baseline_totalaverage)/baseline_totalaverage*100),
    # identify most improved score
    MostImprovedScore = max(percentChange),
    # identify most improved Agent
    MostImprovedAgent = case_when(
      percentChange == MostImprovedScore ~ battery_capacity),
    # calculate difference in improvement of scores from most improved model
    DifferenceInPercentChange = ((percentChange - MostImprovedScore)/MostImprovedScore)*100) %>%
  ungroup() 

```

Regression Analysis: 
```{r, echo=FALSE, message=FALSE}
## Average Score Regression Analysis
reg2.a <- lm(average_score ~ battery_capacity, battery_df)
reg2.b <- lm(average_score ~ battery_capacity + Dirt + Wall, battery_df)
export_summs(reg2.a, reg2.b)
plotResults2 <- effect_plot(reg2, pred = 'battery_capacity', plot.points = TRUE)
plotResults2
```




```{r, echo=FALSE, message=FALSE}
########### Average over all environments
averageperformance_battery <- ggplot(totalaverage, aes(battery_capacity, totalaverage)) + 
  geom_bar(aes(fill = battery_capacity), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title =  "Memory Sucky's Average Scores by Battery Capacity",
       subtitle = "Over All Environments")

averageperformance_battery

########### Low Dirt, High Walls
low_dirt_high_walls_b <- battery_df %>%
  filter(Dirt == .1, Wall == .3) 

low_high_bat <- ggplot(low_dirt_high_walls_b, aes(battery_capacity, average_score)) + 
  geom_bar(aes(fill = battery_capacity), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title =  "Memory Sucky's Average Scores by Battery Capacity",
       subtitle = "Low Dirt, High Walls")

low_high_bat
########### High Dirt, Low Walls
high_dirt_low_walls_b <- battery_df %>%
  filter(Dirt == .3, Wall == .1)

high_low_bat <- ggplot(high_dirt_low_walls_b,  aes(battery_capacity, average_score)) + 
  geom_bar(aes(fill = battery_capacity), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title =  "Memory Sucky's Average Scores by Battery Capacity",
       subtitle = "High Dirt, Low Walls")

high_low_bat

```

```{r, echo=FALSE, message=FALSE}
############################# Supplemental 
########### Low Dirt, Low Walls
low_dirt_low_walls_b <- battery_df %>%
  filter(Dirt == .1, Wall == .1)

low_low_b <- ggplot(low_dirt_low_walls_b,  aes(battery_capacity, average_score)) + 
  geom_bar(aes(fill = battery_capacity), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title =  "Memory Sucky's Average Scores by Battery Capacity",
       subtitle = "Low Dirt, Low Walls")

low_low_b
########### High Dirt, high Walls
high_dirt_high_walls_b <- battery_df %>%
  filter(Dirt == .3, Wall == .3)

high_high_b <- ggplot(high_dirt_high_walls_b, aes(battery_capacity, average_score)) + 
  geom_bar(aes(fill = battery_capacity), 
           width = 0.4, 
           position = position_dodge(width=0.5), 
           stat="identity") +  
  theme(legend.position="top", 
        legend.title =element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title =  "Memory Sucky's Average Scores by Battery Capacity",
       subtitle = "High Dirt, HighWalls")
high_high_b
```






```{r, echo=FALSE, message=FALSE}
###### percent function
percent <- function(x, digits = 2, format = "f", ...) {      
  paste0(formatC(x, format = format, digits = digits, ...), "%")
}

############################################## Table Generation
############################ Total average scores over all environments per agent
avgb <- totalaverage %>%
  group_by(battery_capacity) %>%
  select(battery_capacity, percentChange, DifferenceInPercentChange) %>%
  mutate('Performance Improvment' = case_when(
           percentChange == 0 ~ "Baseline Model",
           percentChange != 0 ~ percent(percentChange)),
         'Improvement Difference' = case_when(
           DifferenceInPercentChange == 0 ~ "Most Improved Model",
           DifferenceInPercentChange == -100 ~ "Baseline Model",
           DifferenceInPercentChange != 0 ~ percent(DifferenceInPercentChange))) %>%
  select(-percentChange, -DifferenceInPercentChange ) 

#sort based on sucky model
# create table
avgtableb <- kable(avgb,
      caption = "Total Average Results Over All Environments",
      booktabs = TRUE) %>% kable_styling(position = "left", font_size = 7)
# ouptut table
avgtableb

############################################## Table Generation
############################# low dirt high walls
lowhigh_b <- low_dirt_high_walls_b %>%
  select(battery_capacity, percentChange, DifferenceInPercentChange) %>%
   mutate('Performance Improvment' = case_when(
           percentChange == 0 ~ "Baseline Model",
           percentChange != 0 ~ percent(percentChange)),
         'Improvement Difference' = case_when(
           DifferenceInPercentChange == 0 ~ "Most Improved Model",
           DifferenceInPercentChange == -100 ~ "Baseline Model",
           DifferenceInPercentChange != 0 ~ percent(DifferenceInPercentChange))) %>%
  select(-percentChange, -DifferenceInPercentChange ) 

# create table
lowhightable_b <- kable(lowhigh_b,
      caption = "Results from Environment with Low Dirt, High Walls",
      booktabs = TRUE) %>% kable_styling(position = "left", font_size = 7)
#output table
lowhightable_b

############################################## Table Generation
################################ high dirt low walls
highlow_b <- high_dirt_low_walls_b %>%
  select(battery_capacity, percentChange, DifferenceInPercentChange) %>%
  mutate('Performance Improvment' = case_when(
           percentChange == 0 ~ "Baseline Model",
           percentChange != 0 ~ percent(percentChange)),
         'Improvement Difference' = case_when(
           DifferenceInPercentChange == 0 ~ "Most Improved Model",
           DifferenceInPercentChange == -100 ~ "Baseline Model",
           DifferenceInPercentChange != 0 ~ percent(DifferenceInPercentChange))) %>%
  select(-percentChange, -DifferenceInPercentChange ) 

# create table
highlowtable_b <- kable(highlow_b,
      caption = "Results from Environment with High Dirt, Low Walls",
      booktabs = TRUE) %>% kable_styling(position = "left", font_size = 7)
# output table
highlowtable_b
```

